Production-maintenance scheduling in complex machinery

### 2024-03-20 Paper.tex
Backup 20/3

\subsubsection{Production-maintenance scheduling} ?????? EXPAND ON THE BACKGROUND ????? This problem belongs to the class of production-maintenance scheduling problems with parallel machines - see Geurtsen et al.~\cite{Production_maintenance_and_resource_scheduling_A_review} for a comprehensive literature review. Many variants of this problem exist and have been studied for decades, albeit less than other more classical problems. The majority of the literature looks at linear variants of this problem (see~\cite{Scheduling_jobs_with_time_resource_tradeoff_via_nonlinear_programming} for a resource-production exception), mostly because physical considerations tend to be ignored in more abstract models. Other authors avoid the nonlinearities by modeling machine failure with a random distribution~\cite{A_decomposition_method_by_interaction_prediction_for_the_optimization_of_maintenance_scheduling, Multi-component_Maintenance_Optimization:_A_Stochastic_Programming_Approach}, sometimes with Markov chains~\cite{Integrated_maintenance_planning_and_production_scheduling_with_Markovian_deteriorating_machine_conditions, markovian_model_liang_2018}. In these stochastic models, a few authors perform Bender's decomposition~\cite{Integrated_production_and_maintenance_scheduling_for_a_single_degrading_machine_with_deterioration-based_failures, Selected_topics_on_integrated_production-scheduling_and_maintenance-planning_problems}.

In $2022$, Pries defended a thesis focusing on decomposition approaches for joint production-maintenance scheduling problems~\cite{Selected_topics_on_integrated_production-scheduling_and_maintenance-planning_problems}. It is the most similar work to this we could find, but it instead considers the machines as single structures, and that they are all identical. Furthermore, the nonlinearities we use to model the degradation, are instead replaced by random failures.

It is also common to heuristically decouple the maintenance and the production decisions, to make the model more tractable~\cite{A_Two-Stage_Framework_for_Power_Transformer_Asset_Maintenance_Management—Part_I:_Models_and_Formulations}. Not performing these decisions at the same time allows the decision horizon for maintenance to be longer, but loses reliability as a result of the assumptions on production.

@@

  In terms of applications, this model can be used for minimizing maintenance costs of power transformer fleets, where the ``product'' is electricity, or in water treatment stations, where the ``product'' is clean water. More abstractly, it can also be understood as production-maintenance scheduling in factories working in parallel with different interacting machines. In this last example, the factories take on the roll of the (pottentially different) machines, and the machines of the (pottentially interacting) components.\\

@@

 The pricing problem can also be interpreted in the context of machine production. The objective function is equivalent to the maximization of the profit of a machine (where the selling price of the product at time $t$ is given by the corresponding dual value). The added valid inequality enforces a cap on production, after which the product can not be sold, simulating markets where there is limited demand.
 A special case of this problem to power transformers was introduced by Dionísio and Pedroso in~\cite{An_Optimization_Model_for_Power_Transformer_Maintenance}.

@@

   We use Farkas' Pricing~\cite[p.~43]{Generic_Branch-Cut-and-Price} for initializing the RMP, and for fixing infeasibilities during the Branch-and-Price process. This technique uses Farkas' Lemma~\cite{Theorie_der_einfachen_Ungleichungen}, by finding a master variable that breaks the Lemma's statement and adding it to the RMP.

@@

\subsubsection{Branching}
  Branching on fractional master variables is inefficient, and branching on the pricing variables is not possible, due to the aggregation of identical subproblems.

@@

In decomposition approaches, solving the different subproblems in parallel can yield large speedups. While it is also possible to use parallelism to increase the speed of the compact formulation (see~\cite{Assessing_the_Effectiveness_of_(Parallel)_Branch-and-bound_Algorithms} for a review), this would take considerably more effort, both from a technical and a theoretical perspective. For this reason, it is our understanding that applying parallelism only to the decomposition approach is not unfair.

@@

\subsubsection{PF} This production-fixing heuristic tries to take advantage of the impact that the production variable has on the model. Given a fixed production vector, the idea is to perform maintenance at the last possible moment, where if any maintenance action were to be delayed by one time period, the solution would be infeasible. This maintenance strategy is called just-in-time maintenance. For a fixed production vector, Constraints~\eqref{con:production_limit} will fix the condition of the components, sans the maintenance. Heuristically, the fixed production vector is chosen given the farkas duals or the actual duals of the current iteration. Assuming a normal distribution with mean and standard deviation provided by these duals, the duals that are more unlikely to happen will be benefited. %Heuristically, the decision of which values the variables should be fixed to is being done with pattern-search (also known as the Hooke-Jeeves method)~\cite{Direct_Search_Solution_of_Numerical_and_Statistical_Problems}, where each variable is independently increased and decreased, and improving moves are saved. The algorithm iterates over all the variables until either a time limit or a local optimum is reached.

Even if we pick the best possible production vector, this heuristic is not optimal. This is due to the interaction between the components when it comes to their degradation, but also to the maintenance implication constraints (\eqref{con:maintenance_implications}). See the following example.

\begin{example}
    Suppose that we are studying machines with two components, \cmss{A} and \cmss{B}, and that the maintenance of the \cmss{B} implies the maintenance of component \cmss{A}. Assume also that we have the best possible production for this heuristic. It may happen that component \cmss{A} is maintained in year $x$, and the \cmss{B} component (and consequently, \cmss{A}) in year $y > x$. However, it is possible that maintaining \cmss{B} in year $x$ also leads to a feasible solution, which would save us one maintenance of the \cmss{A} component. For example, if the total number of periods is $y+1$, it can happen that both components could have been maintained at $x$ and still reached the end without failing. This anticipation of the maintenance gives a solution that is strictly better than the one we started with.

@@

    Note, however, that if the bottom solution is feasible, then it is guaranteed to be an optimal solution. By construction, the original solution tells us that component \cmss{B} requires one maintenance action at $y$ at the latest, and component \cmss{A} also requires one at $x$ at the latest.

@@

Onto the main procedure, $\cmss{PF-heuristic}$, we start by calling $\cmss{getProduction}$ to obtain the production vector, using the dual values given by the current iteration of the master problem. Iterating first over the components and then over the time periods (otherwise the impact that the components have on each others' condition would be incorrect), we compute the condition of the current component for the current time period, as every variable of Constraint~\ref{con:component_degradation} is fixed, sans maintenance. If the resulting condition is incompatible with the production (see Constraint~\ref{con:production_limit}), then maintenance is scheduled. This means setting production to $0$, the condition to its optimal value, and the maintenance variables to $1$, for the duration of component $k$'s maintenance (lines $12-15$). Line $14$ is necessary, since otherwise a component could have started maintenance that it would not be able to finish.

@@

Some details were excluded to make the heuristic more readable. For example, if when reaching line $12$, $x^k_{t^\prime}$ had already been set to $1$, then we know that this heuristic cannot provide a feasible solution, since a component in optimal condition without any production will still require maintenance. This can be either because the other components have a big impact on the degradation, which this heuristic does not consider, or because the instance itself is not feasible.

@@

>>>>

\subsubsection{Production-maintenance scheduling} ?????? EXPAND ON THE BACKGROUND ????? This problem belongs to the class of production-maintenance scheduling problems with parallel machines - see Geurtsen et al.~\cite{Production_maintenance_and_resource_scheduling_A_review} for a comprehensive literature review. Many variants of this problem exist and have been studied for decades, albeit less than other more classical problems. The majority of the literature looks at linear variants of this problem (see~\cite{Scheduling_jobs_with_time_resource_tradeoff_via_nonlinear_programming} for a resource-production exception), mostly because physical considerations tend to be ignored in more abstract models. Other authors avoid the nonlinearities by modeling machine failure with a random distribution~\cite{A_decomposition_method_by_interaction_prediction_for_the_optimization_of_maintenance_scheduling, Multi-component_Maintenance_Optimization:_A_Stochastic_Programming_Approach}, sometimes using Markov Chains to model a discrete set of conditions~\cite{Integrated_maintenance_planning_and_production_scheduling_with_Markovian_deteriorating_machine_conditions, markovian_model_liang_2018, Combined_Maintenance_Scheduling_and_Production_Optimization}. In these stochastic models, a few authors perform Bender's decomposition~\cite{Integrated_production_and_maintenance_scheduling_for_a_single_degrading_machine_with_deterioration-based_failures, Selected_topics_on_integrated_production-scheduling_and_maintenance-planning_problems}.

In his thesis, Pries focuses on decomposition approaches for joint production-maintenance scheduling problems~\cite{Selected_topics_on_integrated_production-scheduling_and_maintenance-planning_problems}, using both Bender's and Dantzig-Wolfe decomposition. As opposed to our work, this one considers the machines as single structures, and that they are all identical. Furthermore, the nonlinearities we use to model the degradation, are instead replaced by random failures.

Jahromi et al. heuristically decouple the maintenance and the production decisions, to make the model more tractable~\cite{A_Two-Stage_Framework_for_Power_Transformer_Asset_Maintenance_Management—Part_I:_Models_and_Formulations}. Not performing these decisions at the same time allows the decision horizon for maintenance to be longer, but loses reliability as a result of the assumptions on production.

@@

  \subsubsection{Applications} This model can be used for minimizing maintenance costs of power transformer fleets, where the ``product'' is electricity, or in water treatment stations, where the ``product'' is clean water. More abstractly, it can also be understood as production-maintenance scheduling in factories working in parallel with different interacting machines. In this last example, the factories take on the roll of the (pottentially different) machines, and the machines of the (pottentially interacting) components.\\

@@

 The pricing problem can also be interpreted in the context of machine production. The objective function is equivalent to the maximization of the profit of a machine (where the selling price of the product at time $t$ is given by the corresponding dual value). The added valid inequality enforces a cap on production, after which the product cannot be sold, simulating markets where there is limited demand.
 A special case of this problem to power transformers was introduced by Dionísio and Pedroso in~\cite{An_Optimization_Model_for_Power_Transformer_Maintenance}.

@@

   We use Farkas' Pricing~\cite[p.~43]{Generic_Branch-Cut-and-Price} for initializing the RMP and for fixing infeasibilities during the Branch-and-Price process. This technique uses Farkas' Lemma~\cite{Theorie_der_einfachen_Ungleichungen}, by finding a master variable that breaks the Lemma's statement and adding it to the RMP.

@@

\subsubsection{Branching}
  Branching on fractional master variables is inefficient, and branching on the pricing variables is not possible, due to the aggregation of identical subproblems - two identical machines might pick different columns in the optimal solution.

@@

In decomposition approaches, solving the different subproblems in parallel can yield large speedups (in the order of $T/t$, where T is the time to solve all subproblems, and t is the time to solve the most difficult subproblem). While it is also possible to use parallelism to increase the speed of the compact formulation (see~\cite{Assessing_the_Effectiveness_of_(Parallel)_Branch-and-bound_Algorithms} for a review), this would take considerably more effort, both from a technical and a theoretical perspective. For this reason, it is our understanding that applying parallelism only to the decomposition approach is not unfair.

@@

\subsubsection{PF} This production-fixing heuristic tries to take advantage of the impact that the production variable has on the model. Given a fixed production vector, the idea is to perform maintenance at the last possible moment, where if any maintenance action were to be delayed by one time period, the solution would be infeasible. This maintenance strategy is called just-in-time maintenance. For a fixed production vector, Constraints~\eqref{con:production_limit} will fix the condition of the components, sans the maintenance. Heuristically, the fixed production vector is chosen given the Farkas' duals or the actual duals of the current iteration. Assuming a normal distribution with mean and standard deviation provided by these duals, the production is going to be benefited the more unlikely high its dual is. %Heuristically, the decision of which values the variables should be fixed to is being done with pattern-search (also known as the Hooke-Jeeves method)~\cite{Direct_Search_Solution_of_Numerical_and_Statistical_Problems}, where each variable is independently increased and decreased, and improving moves are saved. The algorithm iterates over all the variables until either a time limit or a local optimum is reached.

However, even if we pick the best possible production vector, this heuristic is not optimal. This is due to the interaction between the components when it comes to their degradation, but also to the maintenance implication constraints (\eqref{con:maintenance_implications}). See the following example.

\begin{example}
    Suppose that we are studying machines with two components, \cmss{A} and \cmss{B}, and that the maintenance of the \cmss{B} implies the maintenance of component \cmss{A}. Assume also that we have the best possible production for this heuristic. It may happen that component \cmss{A} is maintained in year $x$, and the \cmss{B} component (and consequently, \cmss{A}) in year $y > x$. However, it is possible that maintaining \cmss{B} in year $x$ also leads to a feasible solution, which would save us one maintenance of component \cmss{A}. For example, if the total number of periods is $y+1$, it is not unreasonable that both components could have been maintained at $x$ and still reached the end without failing. This anticipation of the maintenance gives a solution that is strictly better than the one we started with.

@@

    Note that if the bottom solution is feasible, then it is guaranteed to be an optimal solution (for this fixed production vector). By construction, the original solution tells us that component \cmss{B} requires one maintenance action at $y$ at the latest, and component \cmss{A} also requires one at $x$ at the latest.

@@

Onto the main procedure, $\cmss{PF-heuristic}$, we start by calling $\cmss{getProduction}$ to obtain the production vector, using the dual values given by the current iteration of the master problem. Iterating first over the components and then over the time periods (otherwise the impact that the components have on each others' condition would be incorrect), we compute the condition of the current component for the current time period, as every variable of Constraint~\ref{con:component_degradation} is fixed, sans maintenance. If the resulting condition is incompatible with the production (see Constraint~\ref{con:production_limit}), then maintenance is scheduled. This means setting production to $0$, the condition to its optimal value, and the maintenance variables to $1$, for the duration of component $k$'s maintenance (lines $12-15$). Line $11$ is necessary, since otherwise a component could have started maintenance that it would not be able to finish.

@@

Some details were excluded to make the heuristic more readable. For example, if when reaching line $12$ $x^k_{t^\prime}$ had already been set to $1$, then we know that this heuristic cannot provide a feasible solution, since a component in optimal condition without any production will still require maintenance. This can be either because the other components have a big impact on the degradation, which this heuristic does not consider, or because the instance itself is not feasible.

@@

As expected, the decomposition approaches appear advantageous, in comparison to the compact model, when increasing the number of identical machines. On the other hand, having more machines increases the number of pricing problems, and longer time-horizons increase their difficulty, so the compact formulation seems better suited for these instances.

An increase in machine complexity also increases the difficulty of the pricing problems....
